Appendix

### 2024-11-14 paper/appendix.Rmd
Update extinction plots + cleaning targets

```{r}
cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by
  site, b) median values by site (cf Main Methods)", " Pisc: piscivorous, rich.:
species richness, node: node of the food-web corresponding to a trophic species,
prop.: proportion."
)
```

@@

```{r}
rand_sim_cap <- paste0(
  "Simulations of (a) species and (b) nodes extinctions in the metaweb according
  to three scenarios: random extinction sequence, extinction sequence by decreasing order of trophic level,
 extinction sequence by increasing order of trophic level. The black line
 represents the prediction of a GAM model for the random extinction sequences (N = 50)."
)
```

```{r ext, fig.cap=rand_sim_cap}
tar_load(figSext)
knitr::include_graphics(figSext)
```

```{r}
obs_fit_cap <- "Fitted versus observed values from the INLA models estimating
the temporal trends of the food-web structure. The black line depicts the first
bissector. Pearson's correlation coefficients are displayed."
```

>>>>

```{r}
cor_cap <- paste0("Correlation among food-web metrics for a) temporal trends by
  site, b) median values by site (cf Main Methods), c) bioenergetic model.", " Pisc: piscivorous, rich.:
species richness, node: node of the food-web corresponding to a trophic species,
prop.: proportion."
)
```

@@

```{r}
rand_sim_cap <- paste0(
  "Simulations of (b) nodes extinctions in the metaweb according to three
  scenarios: random extinction sequence (grey dots), extinction sequence by
  decreasing order of trophic level, extinction sequence by increasing order of
  trophic level. The black line represents the average prediction of a GAM
  linear model for the 50 random extinction sequences."
)
```

```{r ext, fig.cap=rand_sim_cap}
tar_load(figSext)
knitr::include_graphics(figSext[[1]])
```

```{r}
obs_fit_cap <- "Fitted versus observed values from the linear models estimating
the temporal trends of the food-web structure. The black line depicts the first
bissector. Pearson's correlation coefficients are displayed."
```
